Southampton: Mapping Energy Poverty & Deprivation

### 2021-07-29 mappingSotonEnergyDeprivation.Rmd
typo

2019 Fuel Poverty
```{r Loading in the LSOA 2021 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2019_dt <- as.data.table(readr::read_csv (inFile))
lsoa_fuelpov_2019_dt[, la_name := `LA Name`]
lsoa_fuelpovSoton_2019_dt <- selectSoton(lsoa_fuelpov_2019_dt)
```

>>>>

2019 Fuel Poverty

```{r Loading in the LSOA 2021 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2019_dt <- as.data.table(readr::read_csv (inFile))
lsoa_fuelpov_2019_dt[, la_name := `LA Name`]
lsoa_fuelpovSoton_2019_dt <- selectSoton(lsoa_fuelpov_2019_dt)
```
